Potential impact of seasonal forcing on a SARS-CoV-2 pandemic

### 2020-03-14 manuscript/cover letter.tex

Dear Editors of Eurosurveillance,

@@

We think that these results should be taken into account in the further monitoring of the epidemic, and that they contain important information and implications to the readership of Eurosurveillance.

We hope that you will consider our manuscript for publication through the rapid communication track and look forward to
your correspondence. We use the new name SARS-CoV-2 as suggested by ICTV, but would be happy to change to COVID-19 if needed.

>>>>

Dear Editors of Infectious Diseases,

@@

We think that these results should be taken into account in the further monitoring of the epidemic, and that they contain important information and implications to the readership of Infectious Diseases.

We hope that you will consider our manuscript for publication through the rapid communication track and look forward to
your correspondence.
